---
title: "Developing Data Product Project"
author: "Sriram Cheruvu"
date: "August 7, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview
This project builds a ShinyApp using the IRIS dataset and illustrates how k based clustering works when the user dynamically selects the X and Y variables from the IRIS dataset.In addition, the user is provided with the option to select the cluster size (between 1 to 7 clusters). 

The user can slice and analyse the data in a pair wise format and try different options in specifying the number of clusters.

## Project Instructions
1) Write a shiny application with associated supporting documentation. The documentation should be thought of as whatever a user will need to get started using your application.
2) Deploy the application on Rstudio's shiny server
3) Share the application link by pasting it into the provided text box
4) Share your server.R and ui.R code on github

## Application Hosting
The Shiny application created for this project can be found at:
<https://sricheruvu.shinyapps.io/Application/>

The presentation for this project can be found at:
<http://rpubs.com/sricheruvu/>

## Application User Instructions
The following are the steps the user needs to do to run this application:

1. Identify pairwise clusters in the IRIS dataset by:
    a. Selecting X variable.
    b. Selecting Y variable.
2. Select number of clusters (between 1 to 7 clusters)

Depending on the inputs the app will cluster the observations into the number of clusters specified.

```{r }
summary(iris)
head(iris)
```
For example if the user selects x variable - Sepal.Length and y variable - Sepal.Width along with cluster size of 3, the following kmeans will be generated and graphed.

```{r echo=FALSE, warning=FALSE}
kmeans(iris$Sepal.Length,iris$Sepal.Width, centers=3)
```
The corresponding graph is shown below.
```{r echo=FALSE, warning=FALSE}
plot(iris$Sepal.Length,iris$Sepal.Width,col=3,pch=20,cex=1,points(3, pch=3, cex=4, lwd=2))
```

## Conclusion
We used shiny application to demonstrate how flexible the output can be based on the input parameters selected by the user. Clustering using K means have been used to cluster the data from the IRIS dataset based on the inputs selected.

